%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Important note:
% This template requires the resume.cls file to be in the same directory as the

% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.45in,right=0.75in,bottom=0.45in]{geometry} % Document margins
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Akash Shukla} % Your name
\address{+917619827798,  akashshuklacse@gmail.com, 
\url{https://www.linkedin.com/in/akashshuklacs}} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{WORK EXPERIENCE}
{\bf Senior Software Engineer at Optum, UnitedHealth Group}\hfill {\em  Jan 2022 - Current}
\\ {\bf CDSS Cloud Migration} - {\em Care Delivery Support System | Wellmed}
\\ - Migrated monilith on-premises Spring application with millions of lines of code into logical microservices on a Azure Kubernetes cluster.
\\ - Identified cost optimisation opportunity by migrating fully managed CosmosDB to dedicated Mongo DB Cloud which resulted in \$100,000 in annual infrastructure savings.
\\ - Implemented performance monitoring using elastic APM in order to identify most commonly queried APIS. Reduced api responses by 95 percent by utilising redis to cache most frequently used requests.
\\ - Optimised User Experience on pages with slower APIs by utilising Infinite Scrolling pagination.
\\ - Conducted technical domain specific interviews for Full Stack Engineers.
\\[-0.9em]
\\{\bf Software Engineer at Optum, UnitedHealth Group}\hfill {\em  Jul 2019 - Dec 2022}
\\{\bf Empirical} - {\em Automated Information Extraction from Images}
\\ - Developed a product for automated information extraction from images with 95\% accuracy, leveraging a novel information structuring algorithm integrated with Azure OCR.
\\ - Reduced insurance claims audit time from 50 mins to 6 minutes by integrating the in house information extraction tool to the audit workflow.
\\- Led multiple end to end product releases, while reducing time to build by an avg of 5 percent on every release by automating  deployment, monitoring and alerts. Acted as a POC for client demos and product training.
\\[-0.9em]
\\{\bf Catalyst} - {\em Automated Patient Onboarding and Triage (Java,Swift, Python)}
\\ - Reduced patient waiting time in Optum hospitals by 50 percent by developing and iPad application that utilised facial recognition and insurance card OCR for patient onboarding and triage.
\\ - Saved entire conversion cost of EDI(Electronic Data Interchange) file formats by developing in-house platform for EDI data parsing and conversion.

\end{rSection}

% \begin{rSection}{Publications} 
% \\Plant Leaf Disease Classification using Grid Search Based SVM at 2nd International Conference on Data, Engineering and Applications(IDEA) organized by IEEE(Feb 2020) - \href {https://ieeexplore.ieee.org/document/9170725}{Publication}
% \end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Additional Experience} 
    {\bf Nearmash, Internship:} Developed an Ionic Application for 5 Bangalore Apartment complexes, providing curated event and service listings for the neighborhood.
    \\{\bf Mercenary motorsports, Web development and crowdfunding lead:} Raised 6+ lakhs in 2 months through a crowdfunding campaign for high-performance race karts, developing a website with online payments integration.
    \\{\bf RCubed Club:} Founded a 100+ member computer club that nurtured software development skills through hackathons and seminars, resulting in 3 teams qualifying for ICPC regionals in the first year.
    \end{rSection}
    

%--------------------------------------------------------------------------------
%    Internship And Projects
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Technical Projects}
{\bf Landbank} (Django, SQLite, HTML/CSS) \hfill {\em  March 2018}
\\Designed and implemented a Django-based website for digitizing village land ownership data (10,000+ records) in Jhansi district, providing search and filtering capabilities for 50+ users.

\end{rSection}



%--------------------------------------------------------------------------------
%    Internship And Projects
%----------------------------------------------------------------------------------------------
\begin{rSection}{EDUCATION}

    {\bf Bachelor of Technology in Computer Science and Engineering} \hfill {\em Jul 2015 - May 2019} 
    \\ Bundelkhand Institute of Engineering and Technology, Jhansi
    \\ {\bf Undergraduate Coursework:} Operating Systems; Databases; Algorithms; Programming Languages; Comp Architecture; Engineering Entrepreneurship; Calculus III
    
    
    %Minor in Linguistics \smallskip \\
    %Member of Eta Kappa Nu \\
    %Member of Upsilon Pi Epsilon \\
    
    \end{rSection}

\begin{rSection}{Languages and Technologies}
% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{0em}} l }
Java, Python, TypeScript, AngularJS, Spring, Flask, MSSQL, MongoDB, CI/CD, Git, Linux, Bash \
% \end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------

\end{document} 
